\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}

\begin{document}

\title{Written Assignment 1 (CS6340)}
\author{Aishwarya Asesh (u1063384)}
\maketitle
\raggedright

\textbf {Answer 1: Label each word with correct POS}

(a) The/ART presidential/ADJ election/NOUN will/MOD happen/VERB soon/ADV

(b) Excessive/ADJ drinking/GER can/MOD cause/VERB hepatitis/NOUN

(c) I/PERPRO love/VERB to/INF juggle/VERB and/CONJ blow/VERB up/PART balloons/NOUN

(d) She/PERPRO turned/VERB down/PART an/ART invitation/NOUN to/INF go/VERB to/PREP the/ART party/NOUN

(e) Mary/NOUN was/VERB hiking/VERB up/PREP the/ART incredibly/ADV tall/ADJ mountain/NOUN that/RELPRO is/VERB so/ADV famous/ADJ

(f) Investigators/NOUN finally/ADV found/VERB a/ART smoking/GER gun/NOUN which/RELPRO solved/VERB the/ART mysterious/ADJ crime/NOUN

(g) She/PERPRO must/MOD drive/VERB far/ADV but/CONJ will/MOD not/ADV complain/VERB

(h) He/PERPRO never/ADV gives/VERB up/PART and/CONJ no/ADJ obstacles/NOUN will/MOD stop/VERB him/PERPRO
\\[10pt]
\textbf {Answer 2: ACTIVE and PASSIVE}

(a) The burglar has been taken to prison. - PASSIVE

(b) Adele will be singing at Carnegie Hall. - ACTIVE

(c) The horses are brushed every day. - PASSIVE

(d) The boy was chosen for the soccer team. - PASSIVE

(e) Twelve people were injured by the storm. - PASSIVE

(f) He has cooked a huge feast for her family. - ACTIVE

(g) Tom will have single-handedly eaten the entire pizza! - PASSIVE

(h) I have not slept in 24 hours. - ACTIVE

(i) The plane will be own by a navy pilot. - PASSIVE

(j) The essay was written in red ink. - PASSIVE
\\[10pt]
\textbf {Answer 3: Short story question}

a) Intransitive - drove (S2), opens (S2), was (S5)

b) Transitive - needed (S1), bought (S3), got (S3), took (S4), contained (S4), put (S6), sold (S7)

c) Ditransitive - got (S3), sold (S7)

d) Relative Clause Present - S2, S4

e) (coconut (birthday cake))

f) ((Kansas city) (grocery store)) 
\\[10pt]
\textbf {Answer 4: Subcategorization Frames}
\\[10pt]
(a) confront - 
PP (on)
Example - Richard confronted on past funding for the civil war.
NP
Example - Jury confronted the murderer.
\\[10pt]
(b) protect - 
PP (Against) 
Example - It is believed that organic tea may protect against some fatal diseases.
NP
Example - We should protect our heritage.
\\[10pt]
(c) perch -
PP (on)
Example -  I perched on the bike to ride by the hillside.             
\\[10pt]
(d) joke - 
NP
Example - He joked that he will be a dancer in future.
PP (on)
Example - Celebrities should be conscious while joking on facebook. 
\\[10pt]
(e) write - 
PP (on)
Example - He loves writing on paper.
NP NP
Example - Jimmy writes Kimmy a letter everyday.
\\[10pt]
(f) swallow - 
NP
Example - We should not swallow poisonous stuff. 
PP (against)
Example - John's death was caused due to the food he tried to swallow against the dryness of the throat.
\\[10pt]
(g) pretend - 
PP (on)
Example - Richard pretends on facebook to be a rich guy.
NP
Example - We pretended approbation on the funding issue.
\\[10pt]
(h) choke - 
PP (against)
Example - In the upcoming match, will UCLA choke against Utes Utah?
NP
Example - Jeremy choked Paul.
\\[10pt]

\end{document}
